\documentclass{article}
\usepackage{datetime}

\title{Computer Science Undergraduate Society\\Official Constitution}
\author{Computer Science Undergraduate Society}
\date{\monthname[\the\month] \the\year}

\renewcommand{\labelenumi}{\thesection.\arabic{enumi}. }
\renewcommand{\labelenumii}{\thesection.\arabic{enumi}.\arabic{enumii}. }
\renewcommand{\labelenumiii}{\thesection.\arabic{enumi}.\arabic{enumii}.\arabic{enumiii}. }

\begin{document}
\begin{titlepage}
\maketitle
\end{titlepage}

\tableofcontents
\newpage

\section{Introduction}
\begin{enumerate}
	\item Computer Science Undergraduate Society is the official name of the body. No other name shall refer to the body.
	\item In this constitution,
	\begin{enumerate}
		\item "CSUS" refers to the Computer Science Undergraduate Society.
		\item "CS" refers to the discipline of computer science.
		\item "the department" or "CSD" refers to the CS department at Western University.
		\item "the university" refers to Western University.
		\item "member" refers to a student as defined in Section 3 of this document.
	\end{enumerate}
	\item In this document, the use of "he", "she", "his", "her", or "their" refer equally to any gender.
\end{enumerate}

\section{Mandate}
\begin{enumerate}
	\item CSUS has been established to represent Western University's computer science students and enhance the student experience by:
	\begin{enumerate}
		\item Promoting computer science as an academic discipline;
		\item Connecting students to related university services; and
		\item Providing opportunities for the university's computer students to connect with each other, socially and academically.
	\end{enumerate}
\end{enumerate}

\section{Membership}
\begin{enumerate}
	\item A student is automatically a member of CSUS if they are currently registered as an undergraduate student in the Computer Science department at Western University. This is defined as pursuing a Major or Honor's Specialization in Computer Science, Information Systems, Bioinformatics, or Medical Health Informatics.
	\item A first-year student with the intent to register in one of the aforementioned programs is automatically a member of CSUS.
	\item There will be no fees for membership of CSUS.
\end{enumerate}

\section{Executive Team}
\begin{enumerate}
	\item The Executive Team of CSUS will consist of the following:
	\begin{enumerate}
		\item President;
		\item Vice President (Academic);
		\item Vice President (Social);
		\item Vice President (Communications); and
		\item Vice President (Treasurer).
	\end{enumerate}
	\item The roles of the Executive Team are as follows:
	\begin{enumerate}
		\item The President will:
		\begin{enumerate}
			\item Oversee other executive members in fulfilling their duties;
			\item Select CSUS executive members; and
			\item Schedule CSUS meetings.
		\end{enumerate}
		\item The Vice President (Academic) will:
		\begin{enumerate}
			\item Co-ordinate and plan all academic CSUS events.
		\end{enumerate}
		\item The Vice President (Social) will:
		\begin{enumerate}
			\item Co-ordinate and plan all social CSUS events.
		\end{enumerate}
		\item The Vice President (Communications) will:
		\begin{enumerate}
			\item Compose and send CSUS executive updates to CSUS members;
			\item Compose and post CSUS social media updates;
			\item Design promotional graphics and media;
			\item Work with the department to officially display promotional materials; and
			\item Collect minutes at CSUS meetings, both executive and general.
		\end{enumerate}
		\item The Vice President (Treasurer) will:
		\begin{enumerate}
			\item Apply for and collect funding from the department;
			\item Be responsible for all financial matters of CSUS;
			\item Co-ordinate and plan fundraising events and apparel sales; and
			\item Maintain an up-to-date ledger of CSUS funds.
		\end{enumerate}
	\end{enumerate}
	\item No non-member of CSUS is eligible to fill an executive position in CSUS.
	\item No one executive position will be shared by more than one member of CSUS.
	\item If an executive team member ceases to be a member of CSUS, they are no longer able to serve on the executive team and a successor will be named as per section 7.3.1.
\end{enumerate}

\section{Applications}
\begin{enumerate}
	\item The president is to send out a notice to CSUS members that applications for Executive Team positions, with the exception of the president, are open no later than September 14 each year.
	\item CSUS members are eligible to apply between the notice email and September 28 each year.
	\item The president is to review all applications from CSUS members for each Executive Team position no later than September 28.
	\item The president will select the Executive Team out of the CSUS member applications no later than September 30.
	\item Only CSUS members are allowed to apply for CSUS Executive Team positions, as per Section 3.
	\item Former CSUS Executive Team members are eligible for executive team membership, given that they do not contradict Section 3.
	\item If the president is no longer a member of CSUS, or will not be returning to the university next year, they will name a successor out of the current CSUS Executive Team and grant them the role of president.
\end{enumerate}

\section{Impeachment}
\begin{enumerate}
	\item Any CSUS Executive Team member may be impeached for reasons that include, but are not limited to:
	\begin{enumerate}
		\item the Team member fails to complete their duties listed in Section 4 in a reasonable time-frame, as determined by the other members of the Executive Team;
		\item the Team member is absent from all meetings and activities for an extended duration, as determined by other members of the Executive Team; or
		\item just cause as determined by other members of the Executive Team.
	\end{enumerate}
	\item An executive team member may be impeached by the Executive Team with a three-fifths majority vote.
	\item The impeached individual is unable to vote on impeachment decisions.
	\item An executive team member that is impeached will have all privileges associated with their position revoked within one week of the Executive Team's decision.
\end{enumerate}

\section{Resignation}
\begin{enumerate}
	\item Any CSUS Executive Team member may resign at any time.
	\item Resignation will be in the form of a letter addressed to the CSUS President.
	\item Upon receipt of a letter of resignation, the CSUS Executive Team member's privileges will be revoked within one week, as in clause 7.4.
	\begin{enumerate}
		\item If the resigning party is not the President of CSUS, the President of CSUS will decide upon an interim successor to handle the resigning party's duties.
		\item If a successor cannot be named, the President of CSUS will take applications from the CSUS member body according to Section 4.
		\item If the resigning party is the President of CSUS, the resigning party will name a president to handle duties, as described in clauses 7.3.1 and 7.3.2.
	\end{enumerate}
\end{enumerate}

\section{Agency}
\begin{enumerate}
	\item CSUS is not an agent of the University, the Department, the USC, or any affiliated university service. Its views and actions are not representative of the aforementioned parties.
\end{enumerate}

\end{document}
